%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Yash}{Moar}
\position{Former Software Engineer @ HSBC{\enskip\cdotp\enskip}M.S. in Computer Engineering (May 2027, Virginia Tech)}
\address{Virginia Tech, Blacksburg}

\mobile{(540)-824-9514}
\email{yashmoar@vt.edu}
%\dateofbirth{January 1st, 1970}
% \homepage{www.posquit0.com}
% \github{posquit0}
\linkedin{yash-moar}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \telegram{telegram-username}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``A teacher affects eternity; he can never tell where his influence stops."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Professor [Name]}
  {Bradley Department of Electrical and Computer Engineering\\Virginia Tech\\Blacksburg, VA}
% The date on the letter, default is the date of compilation
\letterdate{}
% The title of the letter
\lettertitle{Graduate Teaching Assistant Interest Statement}
% How the letter is opened
\letteropening{Greetings, Professor [Last Name],}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[In summary]{I welcome the chance to support your course and strengthen student learning in the Bradley ECE Department.}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}
  {Yash Moar~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

% Customize the course code and title before sending.
\lettersection{Intent to Support}
I joined the Bradley Department as an M.S. student in Computer Engineering this fall with a focus on machine learning, 
and I am writing to express my strong interest in the GTA position for \textbf{ECE XXXX - Course Title}.
Having worked in the industry for three years, I have seen how critical a strong conceptual foundation is for engineering success. My goal is to help students bridge that gap between theory and practice.
Currently, I serve as a grader for Dr. Virgilio Centeno on \textbf{ECE 2054 (Applied Electrical Theory)} and \textbf{ECE 3304 (Intro to Power Systems)}, supporting 102 students.
Beyond just grading, I focus on providing \textbf{constructive, actionable feedback} that helps students understand their mistakes. I also assist in managing grading workflows to ensure rapid turnaround times, a standard of efficiency I would bring to your course.
\lettersection{Professional and Project Experience}
Prior to my Master's, I spent three years as a Software Engineer at \textbf{HSBC Technology}. While my primary role involved building large-scale microservices, my most relevant experience for this position was \textbf{mentoring new engineers}.
I redesigned the onboarding curriculum, breaking down complex system architectures into digestible learning modules, which reduced onboarding time by 40\%.
This experience honed my ability to \textbf{explain complex technical concepts clearly} which is a skill directly transferable to explaining course material to students during office hours.
Additionally, my background in creating robust technical documentation ensures I can help maintain high quality lab manuals and assignment specifications.
% Add professor-specific research interests or initiatives here.
\lettersection{Collaboration Opportunities}
I am eager to contribute beyond standard grading duties. I can assist in developing lab exercises,  creating review materials, and holding reliable office hours to support student learning.
I understand that GTA allocations are complex, but I would value your recommendation to the committee if you believe my background would be an asset to your course.
I would welcome the opportunity to meet briefly to discuss how I can support your teaching goals for the upcoming semester.
% While working with systems at such a large scale, I realized the extraordinary computing resources required to fulfill our demands. Given the
% increasing complexity and scale of modern computing tasks, traditional system designs have become
% inadequate, requiring innovations in the software-hardware interface. This realization has sparked my
% interest in studying computer systems in detail and being at the forefront of these innovations. I am
% confident that my comprehensive experience and tenacious work ethic make me an excellent candidate for
% your Laboratory.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
